### 2023-12-22 docs/projects/visual-tools/clay-cider-demo-20231217/index.qmd
rerendering

---
format:
  revealjs: {theme: solarized, navigation-mode: vertical, transition: slide, background-transition: fade, incremental: true, output-file: scratch-revealjs.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="scratch-revealjs_files/md-default13.js" type="text/javascript"></script><script src="scratch-revealjs_files/md-default14.js" type="text/javascript"></script>

# Image processing

<div class="sourceClojure">
```clojure
(ns scratch
  (:require [tech.v3.libs.buffered-image :as bufimg]
            [tech.v3.datatype :as dtype]
            [tech.v3.tensor :as tensor]
            [tech.v3.datatype.functional :as fun]
            [scicloj.noj.v1.vis.image :as vis.image]
            [scicloj.kindly.v4.kind :as kind]))
```
</div>

@@

<img src="scratch-revealjs_files/0.png" style="width:100%;" />

@@

<div><p>\[</p><div style="margin-left:10%;width:110%;"><img src="scratch-revealjs_files/0.png" style="width:100%;" /><img src="scratch-revealjs_files/1.png" style="width:100%;" /></div><p>\]</p></div>

@@

<div><h3>raw image</h3><img src="scratch-revealjs_files/0.png" style="width:100%;" /><h3>darkened image</h3><img src="scratch-revealjs_files/2.png" style="width:100%;" /></div>

@@

<img src="scratch-revealjs_files/3.png" style="width:100%;" />

@@

<img src="scratch-revealjs_files/4.png" style="width:100%;" />

@@

<img src="scratch-revealjs_files/5.png" style="width:100%;" />

@@

<div><p>(</p><div style="margin-left:10%;width:110%;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.7
</code></pre></div><img src="scratch-revealjs_files/6.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.8
</code></pre></div><img src="scratch-revealjs_files/7.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.9
</code></pre></div><img src="scratch-revealjs_files/8.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1
</code></pre></div><img src="scratch-revealjs_files/9.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.1
</code></pre></div><img src="scratch-revealjs_files/10.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.2
</code></pre></div><img src="scratch-revealjs_files/11.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.3
</code></pre></div><img src="scratch-revealjs_files/12.png" style="width:100%;" /></div><p>\]</p></div></div><p>)</p></div>

@@

<div><pre><small><small>source: projects/visual-tools/clay-cider-demo-20231217/notebooks/scratch.clj</small></small></pre></div>

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default13.js" type="text/javascript"></script><script src="index_files/md-default14.js" type="text/javascript"></script>
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>

# Clay & Noj demo: image processing

<div class="sourceClojure">
```clojure
(ns index
  (:require [tech.v3.libs.buffered-image :as bufimg]
            [tech.v3.datatype :as dtype]
            [tech.v3.tensor :as tensor]
            [tech.v3.datatype.functional :as fun]
            [scicloj.noj.v1.vis.image :as vis.image]
            [scicloj.kindly.v4.kind :as kind]))
```
</div>

@@

<img src="index_files/0.png" style="width:100%;" />

@@

<div><p>\[</p><div style="margin-left:10%;width:110%;"><img src="index_files/0.png" style="width:100%;" /><img src="index_files/1.png" style="width:100%;" /></div><p>\]</p></div>

@@

<div><h3>raw image</h3><img src="index_files/0.png" style="width:100%;" /><h3>darkened image</h3><img src="index_files/2.png" style="width:100%;" /></div>

@@

<img src="index_files/3.png" style="width:100%;" />

@@

<img src="index_files/4.png" style="width:100%;" />

@@

<img src="index_files/5.png" style="width:100%;" />

@@

<div><p>(</p><div style="margin-left:10%;width:110%;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.7
</code></pre></div><img src="index_files/6.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.8
</code></pre></div><img src="index_files/7.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.9
</code></pre></div><img src="index_files/8.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1
</code></pre></div><img src="index_files/9.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.1
</code></pre></div><img src="index_files/10.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.2
</code></pre></div><img src="index_files/11.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.3
</code></pre></div><img src="index_files/12.png" style="width:100%;" /></div><p>\]</p></div></div><p>)</p></div>

@@

<div><pre><small><small>source: projects/visual-tools/clay-cider-demo-20231217/notebooks/index.clj</small></small></pre></div>
